Generating Street Maps with Tensor Fields

### 2013-11-04 proposal/proposal.tex
changed 'the authors' to 'we'
Adding where constraints come from

\section{Problem Statement}
Our goal is to generate realistic street maps which based on local geography
such as water boundaries, and which can be easily shaped by user-defined
control points to quickly and easily achieve a desired layout. This has been
achieved in \cite{wonka}. However, their implementation is roughly 100,000
lines of C++, which the authors found difficult to understand due to a lack
of modularity. We propose that by implementing the core functionality of this
pipeline in a clear and modular way, we will enable future contributors
to comprehend and build more easily upon this work.

@@

\section{Obstacles}
At present, we are unfamiliar with tensor fields and their associated
operations. We identify this as the primary challenge to the completion of this
project. However, we are confident that, with our background knowledge of
mathematics and the wealth of available resources on the topic, we will be able
to implement the necessary representations and operations of tensor fields to
solve the problem as a whole.

>>>>

\section{Problem Statement}
Our goal is to generate realistic street maps which based on local geography
such as water boundaries, and which can be shaped by user-defined
control points to quickly and easily achieve a desired layout. This has been
achieved in \cite{wonka}. However, their implementation is roughly 100,000
lines of C++, which we found difficult to understand due to a lack
of modularity. We propose that by implementing the core functionality of this
pipeline in a clear and modular way, we will enable future contributors
to comprehend and build more easily upon this work.

@@

\section{Obstacles}
At present, we are unfamiliar with tensor fields and their associated
operations. We identify this as the primary challenge to the completion of this
project. However, we are confident that, with our background knowledge of
mathematics and the wealth of available resources on the topic, we will be able
to implement the necessary representations and operations of tensor fields to
solve the problem as a whole.
\par
We do not anticipate developing a user interface as our first priority, so users
will specify constraints by writing a hardcoded file with their desired 
specifications.
